Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-30 paper.qmd
Change the table properties

# Create the table
kable(notation_df, format = "latex", booktabs = TRUE, escape = FALSE, 
      caption = "Notations used in this paper.", label = "tbl-notations") |>
  kable_styling(full_width = FALSE) |>
  row_spec(0, bold = TRUE)
```

>>>>

# Create the table
kable(notation_df, format = "latex", booktabs = TRUE, escape = FALSE, 
      caption = "Notations used in this paper.", label = "tbl-notations") |>
  kable_styling(latex_options = c("HOLD_position"), position = "center", full_width = FALSE) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:2, width = c("5cm", "12cm"))
```
